---
title: "Data Science and R for Investors"
output: html_notebook
---

# Data Science and R for Investors
```{r}
library(tidyverse)
library(tidyquant)
library(timetk)
library(tibbletime)
library(scales)
library(highcharter)
library(broom)
library(PerformanceAnalytics)
```

# Strategy
  + Buy when the SP500 50-day SMA is above the 200-day SMA ('golden cross'')
  + Sell when the 50-day SMA moves below the 200-day SMA ('death cross')
  + Code up the strategy
  + Visualize its results and descriptive statistics
  + Compare it to buy and hold
  + Add secondary logic, visualize that strategy
  + Conclude by building a Shiny dashboard for further exploration

# Remark on data science work flow
  1. Import
  2. Tidy
  3. Transform - Visualize - Model (iterative cycle)

# Import data
We will be working with SP500 and treasury bills data so that when we exit the SP500 we can invest in treasuries and get some return.

We can use the 'tidyquant'package and its tq_get() function to grab data from Yahoo! Finance.

```{r}
symbols <- c("^GSPC", "^IRX") #Note: c() means concatenate into a vector

prices <- 
  tq_get(symbols,
        get = "stock.prices",
        from = "1990-01-01")
        
head(prices)
```

It is also possible to import data from an Excel or csv file.

```{r, eval = FALSE}
prices_excel <- 
  read_excel("~datasets/ib-prices.xlsx") %>%
  mutate(date = ymd(date))
```

```{r, eval = FALSE}
prices_csv <- 
  read_csv("ib-prices.csv") %>%
  mutate(date = ymd(date))
```

# Let's plot the price of the SP500 using highcharter
```{r}
library(highcharter)
prices %>%
  filter(symbol == "^GSPC") %>%
  hchart(.,
         hcaes(x = date, y = adjusted),
         type = "line") %>%
  hc_title(text = "GSPC price")
```

